---
title: "hw6"
author: "Dmitriy Tsimokha"
date: "2/28/2021"
output: 
  html_document:
    fig_width: 10
    fig_height: 7
---
<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
</style>
---

1.  Get data from read.dta("[https://stats.idre.ucla.edu/stat/stata/dae/nb_data.dta"](https://stats.idre.ucla.edu/stat/stata/dae/nb_data.dta"):));

    -   *gender* -- gender of the respondent (female, male)
    -   *math* -- score on math test
    -   *daysabs* -- number of days absent
    -   *prog* -- type of program\
        *(use as factor; 1 -- vocational, 2 -- general, 3 -- academic)*

2.  Predict **math test scored** by *gender*, *number of missed days* and the *program type*

3.  Test for **overdispersion** and **zero-inflation**.\
    Choose the appropriate model

4.  Interpret the coefficients

5.  Look at the model fit

```{r}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
library(foreign)
df <- read.dta("https://stats.idre.ucla.edu/stat/stata/dae/nb_data.dta")
df$prog <- as.factor(df$prog)
df <- na.omit(df)
```

## Predict math test scored by gender, number of missed days and the program type.

```{r}
mpois = glm(math ~ gender + daysabs + prog, data = df, family = poisson)
summary(mpois)
```

All p-values for regressors show significant influence - *that's great*

## Test for overdispersion and zero-inflation.

```{r}
library(AER)
# linear
dispersiontest(mpois, trafo = 1)
```

Mean and variance are not equal and overdispersion is definitely exists in the model.

```{r}
# quadratic
dispersiontest(mpois, trafo = 2)
```

Looks like better to choose quadratic relationship model.

Basing on overdispersion and zero-inflation tests I prefer to choose quadratic model.

```{r}
fm_qpois <- glm(math ~ gender + daysabs + prog, data = df, family = quasipoisson)
fm_nb <- MASS::glm.nb(math ~ gender + daysabs + prog, data = df)
library(texreg)
screenreg(list(mpois, fm_qpois, fm_nb))
```

But now looks like that **NB** is even better than quadratic!

```{r zero-inflation}
library(vcdExtra)
zero.test(table(df$math))
```

Zero-inflation test looks very strange 🤔

```{r}
sum(df$math==0)
```

So my dataframe does not contain any zeros, *I have zero of zeros in dependent variable* - **zero-inflation** is not applicable.

## Interpreting coefficients

```{r}
library(mfx)
negbinmfx(math ~ gender + daysabs + prog, data = df)
```

-   **gender**: \
    🔽 men have **2.23**% lower *scores on math* than women

-   **daysabs**: \
    🔽 every additional day of absence decreases the score on math by **0.75**%

-   **prog**:\
    🔽 for '**general**' type of program in comparison with 'vocational' type the score on math decreases by **4.8**%\
    🔼 for '**academic**' type of program in comparison with 'vocational' type the score on math increases by **7.5**%

## Model fit

```{r}
library(pscl)
t(pR2(fm_nb))
```

McFadden's pseudo R\^2 shows that *in terms of fitness you have no fitness* 😒
