---
title: "hw5"
author: "Dmitriy Tsimokha"
date: "2/28/2021"
output: 
  html_document: 
    fig_width: 10
    fig_height: 7
---
<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
</style>
---

Use data frame '*uk'* from '*seminar2 (2).RData*'

The variables are:

-   ***polintr***: how interested in politics;\
    from *1 - Not at all interested* to *4 - Very interested*

-   ***age***: age of the respondent

-   ***sex***: gender of the respondent

-   ***edu***: age when completed education

-   ***income1***: income group

Fulfill the following tasks:

1.  Predict **interest in politics** by *age*, *gender*, *education* and *income grou*p.
2.  Interpret the coefficients.
3.  Tell if the model fits data well.
4.  Visualize the link between interest in politics and age when respondent completed education.

```{r}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
load('seminar2 (2).RData')
```

## Predict interest in politics by age, gender, education and income group

```{r}
library(MASS)
m1 = polr(polintr ~ age + sex + edu + income1, data = uk, Hess=T)
summary(m1)  # logit
```

```{r eval=FALSE, include=FALSE}
m2 = polr(polintr ~ age + sex + edu + income1, data = uk, method = "probit")
summary(m2)  # probit
```

## Interpret the coefficient

```{r eval=FALSE, include=FALSE}
exp(coef(m1))  # logit
```

Better to interpret only AME coefficients:

```{r}
library(knitr)
#Marginal effects
library(erer)
#ocME(m1)  # logit
kable(ocME(m1)$out$ME.all*100)  # in percent
```

-   **age**: each year the probability of being...

    -   🔽 '*Not at all interested*' in politics in comparison with other options decreases by **0.3**%
    -   🔽 '*Not at all interested*' or '*Hardly interested*' in politics in comparison with other options decreases by **0.2**%
    -   🔼 '*Not at all interested*', '*Hardly interested*' or '*Quite interested*' in politics in comparison with being '*Very interested*' increases by **0.3**%
    -   🔼 '*Very interested*' in politics in comparison with all previous options increases by **0.2**%

-   **sex**: for women the probability of being...

    -   🔼 '*Not at all interested*' in politics compared to other options is **6.7**% higher than for men
    -   🔼 '*Not at all interested*' or '*Hardly interested*' in politics compared to other options is **5.1**% higher than for men
    -   🔽 '*Not at all interested*', '*Hardly interested*' or '*Quite interested*' in politics compared to being '*Very interested*' is **7.3**% lower than for men
    -   🔽 '*Very interested*' in politics in compared with all previous options is **4.5**% lower than for men

-   **edu**: each year the probability of being...

    -   🔽 '*Not at all interested*' in politics in comparison with other options decreases by **1.9**%
    -   🔽 '*Not at all interested*' or '*Hardly interested*' in politics in comparison with other options decreases by **1.5**%
    -   🔼 '*Not at all interested*', '*Hardly interested*' or '*Quite interested*' in politics in comparison with being '*Very interested*' increases by **2.2**%
    -   🔼 '*Very interested*' in politics in comparison with all previous options increases by **1.3**%

-   **income1**: per each increase in income group the probability of being...

    -   🔽 '*Not at all interested*' in politics in comparison with other options decreases by **1.5**%

    -   🔽 '*Not at all interested*' or '*Hardly interested*' in politics in comparison with other options decreases by **1.2**%

    -   🔼 '*Not at all interested*', '*Hardly interested*' or '*Quite interested*' in politics in comparison with being '*Very interested*' increases by **1.7**%

    -   🔼 '*Very interested*' in politics in comparison with all previous options increases by **1.0**%

```{r eval=FALSE, include=FALSE}
#ocME(m2)  # probit
kable(ocME(m2)$out$ME.all)
```

## Tell if the model fits data well

```{r}
library(pscl)
t(pR2(m1))
```

Model seems to be obsolete to predict anything - McFadden's pseudo R\^2 equals to 0.05 which is too low - *what a shame*.

```{r}
hitmiss(m1)
```

So model with predictors is just slightly better than null model and guess even worse than random guessing - *that's a pity*.

## Visualize the link between interest in politics and age respondent completed education

```{r}
library(sjPlot)
plot_model(m1, type = "emm", terms = "age", title = 'Logit')
#plot_model(m2, type = "emm", terms = "age", title = 'Probit')
```

Relationship of **age** and **polintr** looks like *linear-ish* and people with age tends to be more interested in politics.
