---
title: "hw6"
author: "Dmitriy Tsimokha"
date: "2/28/2021"
output: 
  html_document:
    fig_width: 10
    fig_height: 7
---

```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
</style>
```
```{r}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
load('test_2.RData')
```

# Task 1

*test_2.RData* contains data frame *'culture'* which includes the following variables:

-   c.act.n -- number of cultural activities that the respondents participated in the last 12 months

-   gender -- gender of the respondent

-   age -- age in years

-   edu -- age when completed education

-   bill -- if the respondent has difficulties paying bills

-   commun -- area of residence

-   country -- country where the respondent lives

1.  Choose only observations from **Bulgaria**.
2.  Choose an appropriate model to predict the number of cultural activities by gender, age, education, problems paying bills, and area of residence.
3.  Interpret the coefficients, comment on the results.
4.  Check model fit, comment on the results.

```{r}
df <- culture[culture$country=='Bulgaria',]
```

```{r}
# nothing can be better than usial OLS model
model <- lm(data = df, formula = 'c.act.n ~ gender + age + edu + bill + commun')
summary(model)
```

Overall, model has moderate prediction \~ **0.31**.

Only for *Small/middle town* coefficient is insignificant, all other predictors doing their jobs quite well:

-   🔼 for **females** number of attended cultural activities **higher** on **0.57**

-   🔽 for **each additional year of age** number of attended cultural events **lowers** for **0.03**

-   🔼 for **each additional year of education** number of attended cultural events **highers** for **0.2**

-   🔼 those who **doesn't have problems with bill paying** have number of attended cultural events **higher** on **0.7** in comparison with those who have such problems (*maybe because of amount of free money to spend?*)

-   🔼 and for **people from large towns** number of attended cultural events **higher** on **1.15** (*supposedly because of amount, variety and availability of such events in big towns*)

# Task 2

*test_2.RData* contains data frame *'ess'* which includes the following variables:

-   *atcherp* -- And how emotionally attached do you feel to Europe: 1- Not at all emotionally attached, 11 -- Very emotionally attached

-   *age* -- age of the respondent in years

-   *incdcl* -- income decile: 1 - the lowest decile, 10 -- the highest

-   *gndr* -- gender of the respondent: male, female

-   *cntry* -- country

-   *gdp* -- GDP per capita

1.  Specify the empty model of the attachment to Europe varying by
    country. Calculate ICC. Do the views vary considerably across the
    countries?
2.  Include individual level predictors into your model. Interpret the
    coefficients.
3.  Randomize the coefficient for income. Do the coefficients vary across
    the countries? Consider variable transformations if necessary.
4.  Include GDP per capita into the model. Consider transformation of
    this variable. Interpret the result.
5.  Check if the effect of income differs depending on the country
    economic development.
6.  Visualize the effects in the final model. Interpret the results.
7.  Check if the model fits the data well.

```{r}
library(lme4); library(texreg); library(sjstats); library(sjPlot)
```

```{r}
# null model
m0 = lmer(atcherp ~ 1|cntry, data = ess)
summary(m0)
```

Violetta, sorry, I was trying to do the test while working and not succeeded with that - my people need me on the work :(
