---
title: "hw7"
author: "Dmitriy Tsimokha"
date: "08.03.2021"
output: 
  html_document:
    fig_width: 10
    fig_height: 7
---

```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
</style>
```

::: {.flowers aria-hidden="true"}
::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::

::: {.flower}
🌸
:::
:::

```{css echo = FALSE}
/*Source: https://codepen.io/codeconvey/pen/xRzQay*/
.flower {
  font-size: 50px;
  font-family: Arial;
  text-shadow: 0 0 1px #000;
}
@-webkit-keyframes flowers-fall{0%{top:-10%}100%{top:100%}}
@-webkit-keyframes flowers-shake{
    0%{-webkit-transform:translateX(0px);transform:translateX(0px)}
   50%{-webkit-transform:translateX(80px);transform:translateX(80px)}
  100%{-webkit-transform:translateX(0px);transform:translateX(0px)}}
@-webkit-keyframes rotation {
    0% {-webkit-transform:rotate(0deg); transform:rotate(0deg)}
    100% {-webkit-transform:rotate(360deg);transform:rotate(360deg)}
}
@keyframes flowers-fall{
    0%{top:-10%}
  100%{top:100%}}
@keyframes flowers-shake{
    0%{transform:translateX(0px)}
   50%{transform:translateX(80px)}
  100%{transform:translateX(0px)}}
@keyframes rotation {
    0% {transform:rotate(0deg)}
    100% {transform:rotate(360deg)}
}
.flower{
  position:fixed;
  top:-10%;
  z-index:9999;
  -webkit-user-select:none;
  -moz-user-select:none;
  -ms-user-select:none;
  user-select:none;
  cursor:default;
  -webkit-animation-name:flowers-fall,flowers-shake,rotation;
  -webkit-animation-duration:10s,3s,10s;
  -webkit-animation-timing-function:linear,ease-in-out,linear;
  -webkit-animation-iteration-count:infinite,infinite,infinite;
  -webkit-animation-play-state:running,running,running;
  animation-name:flowers-fall,flowers-shake,rotation;
  animation-duration:10s,3s,10s;
  animation-timing-function:linear,ease-in-out,linear;
  animation-iteration-count:infinite,infinite,infinite;
  animation-play-state:running,running,running}
.flower:nth-of-type(0){left: 1%;-webkit-animation-delay:  0s,  0s;animation-delay:  0s,  0s}
.flower:nth-of-type(1){left:10%;-webkit-animation-delay:  1s,  1s;animation-delay:  1s,  1s}
.flower:nth-of-type(2){left:20%;-webkit-animation-delay:  6s,0.5s;animation-delay:  6s,0.5s}
.flower:nth-of-type(3){left:30%;-webkit-animation-delay:  4s,  2s;animation-delay:  4s,  2s}
.flower:nth-of-type(4){left:40%;-webkit-animation-delay:  2s,  2s;animation-delay:  2s,  2s}
.flower:nth-of-type(5){left:50%;-webkit-animation-delay:  8s,  3s;animation-delay:  8s,  3s}
.flower:nth-of-type(6){left:60%;-webkit-animation-delay:  6s,  2s;animation-delay:  6s,  2s}
.flower:nth-of-type(7){left:70%;-webkit-animation-delay:2.5s,  1s;animation-delay:2.5s,  1s}
.flower:nth-of-type(8){left:80%;-webkit-animation-delay:  1s,  0s;animation-delay:  1s,  0s}
.flower:nth-of-type(9){left:90%;-webkit-animation-delay:  3s,1.5s;animation-delay:  3s,1.5s}
```

# C 8 марта, Виолетта!

```{r}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
library(lme4); library(texreg); library(sjstats); library(sjPlot)
load('Europe2.RData')
load('imm23.RData')
```

• Vary the effect of parents' education among the schools. Check if the

random slope model is better.

```{r}
# null model
m0 = lmer(MATH ~ 1|SCHID, data = data)
summary(m0)
```

```{r}
m1 = lmer(MATH~SES+WHITE+HOMEWORK+PARENTED+SEX+(1|SCHID), data = data)
m2 = lmer(MATH~SES+WHITE+HOMEWORK+PARENTED+SEX+(1+PARENTED|SCHID), data = data)
anova(m1, m2)
```

Random slope model for PARENTED is better - p-value \< 0.5

• Check if the type of school affects the results in math.

```{r}
m3 = lmer(MATH~SES+WHITE+HOMEWORK+PARENTED+SEX+PUBLIC+(1+PARENTED|SCHID), data = data)
screenreg(m3)
```

Type of school has no significant effect on math.

• Check if the effect of parental education differs depending on the

school type.

```{r}
m4 = lmer(MATH~SES+WHITE+HOMEWORK+PARENTED+SEX+MEANSES+PARENTED*PUBLIC+(1+PARENTED|SCHID), data = data)
screenreg(m4)
```

Interaction effect of parental education and school type is not significant.

• Indicate which school has the lowest impact of parents' education.

```{r}
# random effects
re <- ranef(m2)
# add beta from model to HOMEWORK to obtain true beta-coef per school
re$SCHID$PARENTED = 2.53+re$SCHID$PARENTED
re$SCHID[which.min(abs(re$SCHID$PARENTED - 0)),]
```

School with ID 62821 has the lowest impact of parent's education

• Plot the effects of your final model.

```{r}
# fixed effects
plot_model(m2, type = 'est')
```

```{r}
# random effects
plot_model(m2, type = 're', sort.est = 'PARENTED')
```

• Plot the interaction term and comment on the results

```{r}
plot_model(m4, type = "pred", terms = c("PARENTED", "PUBLIC"))
```

**Interaction effect is not significant** nevertheless seems that for public schools parental education have greater slope and increase in parental education can cause greater increase in math while intercept is slightly lower.

• Calculate R2.

```{r}
performance::r2(m2)
```
